Semantic prediction in {R}ussian

### 2020-04-10 paper.tex
introduce linebreak in author line
hyperlinks fixed

\documentclass[a4paper]{article}
\usepackage{lrec}
\usepackage{amsmath}
\usepackage{polyglossia}
\usepackage{graphicx}

@@

\name{Anastasia Nikiforova, Sergey Pletenev, Daria Sinitsyna,
Semen Sorokin, Anastasia Lopukhina, Nicholas Howell}
\address{National Research University Higher School of Economics \\ Moscow,
Russian Federation}

\begin{document}

\maketitleabstract

>>>>

\documentclass[a4paper]{article}
\usepackage{lrec}
\usepackage{amsmath}
\usepackage{polyglossia}
\usepackage{graphicx}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

@@

\name{\begin{tabular}{l}Anastasia Nikiforova, Sergey Pletenev, Daria
Sinitsyna, \\
Semen Sorokin, Anastasia Lopukhina, Nicholas Howell\end{tabular}}
\address{National Research University Higher School of Economics \\ Moscow,
Russian Federation}

\begin{document}
\hypersetup{allcolors = blue}
\maketitleabstract
